---
title: "The CircTarget package - Explore the circRNAs-Target expression profiling molecular pathways"
author: 
  - name: Alessia Buratin
    affiliation: Departement of Biology, Department of Molecular Medicine, University of Padova
date: "`r format(Sys.Date(), '%m/%d/%Y')`"
output: rmarkdown::html_vignette
abstract: |
  *CircTarget* provides a strategy to analyze circular and linear transcriptome rely on data mining and statistical learning techniques. *CircTarget* package offers a tidy pipeline, starting from the provided circRNA-Target which expression classifies samples with high and low expression of it, a comprensive transcriptome and molecular pathway analysis are performed, including visualisation, normalization, classification, clustering, Differential Expression Analysis and Gene Set Enrichment Analysis. The package accepts data presented as a matrix of raw counts and allows the inclusion of variables that occur with the experimental setting. A series of functions enables data cleaning by filtering rows, data adjustment by identify and removing the unwonted source of variation and to select the best predictors for modeling the responce variable. A learning technique is applied to build a robust classification model, and also an unsupervised analysis is carried out to gain mechanistic insights and detect the molecular pathway associated with the expression levels of the Target circRNA. Finally, a Differential Expression Analysis identyfied deregulated mRNAs and a GSEA is performed for them. *CircTarget* stands for "circRNA-Target".
  CircTarget package version: `r packageVersion("CircTarget")`
vignette: >
  %\VignetteIndexEntry{CircTarget}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<style>
    body {
        max-width: 1500px;
        text-align: justify
    }
    .page-header {
      background-image: none;
      background-color: #ff7600;
    }
    .main-content h2 {
      color: #ff7600;
    }
</style>


## Overview

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

# Quickstart

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
